Design of Blur Invariant Fiducial for Low Cost Quadcopter

### 2014-01-28 ECCV/paper.tex
1. Added connected components 2. workaround for complex kernel in Gabor filter

\section{Introduction}
\subsection{Motivation}
\section{Related Work}
ARToolkit \cite{ARToolkit02} /ARTag \cite{Fiala05} \\
Pi-Tag \cite{Pitag13} \\
Blut \cite{Wu:2011}
\section{Our Contribution}
\subsection{Fiducial Detection}

@@

\clearpage\mbox{}Page \thepage\ of the manuscript.
\clearpage\mbox{}Page \thepage\ of the manuscript.
\clearpage\mbox{}Page \thepage\ of the manuscript.
\clearpage\mbox{}Page \thepage\ of the manuscript.
\clearpage\mbox{}Page \thepage\ of the manuscript.
\clearpage\mbox{}Page \thepage\ of the manuscript.
This is the last page of the manuscript.
\par\vfill\par
Now we have reached the maximum size of the ECCV 2012 submission.
\end{document}

>>>>

\section{Introduction}

\subsection{Motivation}
Tracking vehicle by an autonomous vehicle. \\
Fiducials for tracking under motion blur.

\section{Related Work}
ARToolkit \cite{ARToolkit02} /ARTag \cite{Fiala05} \\
Pi-Tag \cite{Pitag13} \\
Blut \cite{Wu:2011}

\section{Our Contribution}

\subsection{Design of Fiducial}

\subsection{Fiducial Detection Algorithm}
Apply Gabor Filter on input image \\
Find Connected components in Gabor output \\
Cluster the connected components \\
Merge the clusters \\
Detect code in the bounding box \\
Classify the detected code

@@

\end{document}
